Trending assessment for nowcasts, measurements, and forecasts

### 2024-02-12 paper.tex
Update on Overleaf.
Add first plots for ed arrival application
Change labels and add math notation

%%% --- Tabulars
\usepackage{booktabs}
\usepackage{multirow} % cells over several rows
\usepackage{tabularx}
\usepackage{tabularray}

@@

\newcommand{\lag}[1][l]{\Delta_{#1}}
\DeclarePairedDelimiter{\abs}\lvert\rvert
\DeclareMathOperator{\sign}{sign}
\newcommand{\tmax}{\bar{t}}
\newcommand{\ind}[1]{\mathbbm{1}\{#1\}}
\newcommand{\ydiff}{D y}
\newcommand{\ydifft}{Dy^\star}
\newcommand{\xdiff}{Dx}
\newcommand{\xdifft}{Dx^\star}
\newcommand{\Ydiff}{DY}
\newcommand{\Xdiff}{DX}
\newcommand{\Prob}[1]{P(#1)}
\newcommand{\mprob}{\tilde{m}}
\newcommand{\Ber}{\text{Ber}}
\newcommand{\SBer}{\text{SBer}}
\newcommand{\cond}{\:\lvert\:}

@@

\title{Assessment and Optimization of Nowcast Measures for Trend Detection}
\author{Oliver Grothe, Bolin Liu, Jonas Rieger}

@@

\section{Introduction}

\begin{itemize}
    \item 
\end{itemize}

\section{Trending assessment}

\begin{itemize}
    \item Es interessiert uns $P(x y) > 0$
    \item 
\end{itemize}

>>>>

%%% --- Tabulars
\usepackage{booktabs}
\usepackage{multirow} % cells over several rows
\usepackage{tabularx}
%\usepackage{tabularray}

@@

\DeclarePairedDelimiter{\abs}\lvert\rvert
\DeclareMathOperator{\sign}{sign}
\newcommand{\tmax}{\bar{t}}
\newcommand{\ind}[1]{\mathbbm{1}\{#1\}}
\newcommand{\Prob}[1]{P(#1)}
\newcommand{\cond}{\:\lvert\:}

\newcommand{\R}{\mathbb{R}}
\newcommand{\SBer}{\text{SBer}}

\newcommand{\diffxl}{\mathbf{x}^{\Delta,l}}
\newcommand{\diffyl}{\mathbf{y}^{\Delta,l}}
\newcommand{\diffx}{\mathbf{x}^{\Delta}}
\newcommand{\diffy}{\mathbf{y}^{\Delta}}
\newcommand{\diffxlt}{\mathbf{x}^{\Delta,l}_t}
\newcommand{\diffylt}{\mathbf{y}^{\Delta,l}_t}
\newcommand{\diffxt}{x^{\Delta}_t}
\newcommand{\diffyt}{y^{\Delta}_t}

\newcommand{\acc}{\mu}
\newcommand{\acceps}{\acc_{\eps}}
\newcommand{\accpeps}{\acceps^+}
\newcommand{\accmeps}{\acceps^-}
\newcommand{\accp}{\acc^+}
\newcommand{\accm}{\acc^-}

@@

\title{Trending assessment for nowcasts, measurements, and forecasts}
\author{Oliver Grothe, Bolin Liu, Jonas Rieger}

@@

Agenda für heute:
\begin{itemize}
    \item Aufteilung
    \begin{itemize}
        \item Introduction (1.5 pages), Conclusion (0.5 pages), Abstract
        \item Nowcasting (1 pages): Bolin
        \item Trending (5-6 pages): Jonas fängt an
        \item Application (5-6 pages): Jonas
    \end{itemize}
    \item Datenquellen
\end{itemize}

\begin{itemize}    
    \item Journal/Anwendungsgebiet klären: Angewandtes Medizin Statistikjournal? Dann müsste man die folgenden Abschnitte entsprechend ausrichten
\end{itemize}

\section{Introduction}\label{sec:introduction}

\input{sections/01-introduction}

\section{Application areas and Notation} \label{sec:notation}

\input{sections/02-notation}

\section{Trending assessment}\label{sec:trending}

\input{sections/03-trending}

%\section{Simulation Studies (?)}
%
%Eher nicht, weil angewandtes Paper

\section{Application to real-world data} \label{sec:application}

\input{sections/04-application}

\printbibliography

### 2024-02-12 sections/02-notation.tex
Change labels and add math notation

All the measures discussed, regardless of the area, have in common that the comparison and evaluation of the methods takes into account the local absolute differences in different ways, but does not directly consider the influence of the sign of the differences. To our best knowledge, there is no work in the literature that addresses the trending capability of measurement series or prediction with continuous outcomes. Because of the different ways in which data are generated and processed depending on the area of application, the data collected should be prepared in different ways for further processing in order to identify the trending ability (see chapter \ref{cap: trending}). In particular, the following shows how the time series of change (with lag $l$) should be defined, depending on whether measurement, forecasting or nowcasting methods are considered.

@@

\todo[inline]{Formeln als Tabelle oder in den Text einbinden.}

>>>>

All the measures discussed, regardless of the area, have in common that the comparison and evaluation of the methods takes into account the local absolute differences in different ways, but does not directly consider the influence of the sign of the differences. To our best knowledge, there is no work in the literature that addresses the trending capability of measurement series or prediction with continuous outcomes. Because of the different ways in which data are generated and processed depending on the area of application, the data collected should be prepared in different ways for further processing in order to identify the trending ability (see chapter \ref{sec:trending}). In particular, the following shows how the time series of change (with lag $l$) should be defined, depending on whether measurement, forecasting or nowcasting methods are considered.

@@

\todo[inline]{Formeln als Tabelle oder in den Text einbinden.}
\todo[inline]{$\mathbf{y}$ definieren.}
